Twists of supersymmetric gauge theories

### 2019-08-18 paper.tex
Added a reference

\begin{definition}
\chris{The definition of the Chevalley-Eilenberg complex with coefficients, in particular the cup product / bracket, with its correct sign.}
\end{definition}

>>>>

\begin{definition}
\chris{The definition of the Chevalley-Eilenberg complex with coefficients, in particular the cup product / bracket, with its correct sign.  Pavel suggested saying that $C^\bullet(\gg; V) = \hom(\sym^\bullet(\gg[1]), V)$, and following the sign rule he used in \cite[Section 2.1]{SafronovCoisoInt}.}
\end{definition}
